Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-23 paper/v2/paper-edited.tex
Edit name
space saving changes

\author{%
Ryan Beckett\\
  \affaddr{Princeton}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{UCLA}
  %\affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and
Jitu Padhye\\
  \affaddr{Microsoft}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton}
  %\\
  %\email{dpw@princeton.edu}
}

@@

The next step rewrites the high-level constraints such as $\Enter$ according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $r \cdot (s \Prefer t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator. In general, we employ the following distributivity equivalences:
%
\[
\begin{array}{c}
  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
\end{array}
\]
%
where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
%
In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ and $t \cdot u$ is preferred. \sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
%
\sysname also rejects policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) as invalid.

@@

%It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
%even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$. To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$). It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.

@@

As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur. Determining when this can happen requires knowledge, not only of the topology, but also of the policy. For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated. If that one link fails, a black hole might be introduced.
%
Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.

@@

@@

For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the simplified PGIR. Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knows that 2 is a lower bound on the number of failures required to potentially introduce an aggregation black hole for prefix \CD{PG1}. This process is repeated for other aggregation locations (\EG, $Y$).

@@

Finally, the external AS $W$ should prefer our internal router $A$ over $B$. In general, it is not possible to reliably control traffic entering the network beyond certain special cases. In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$. Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic. The compiler can perform a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default. Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.

After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on. In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from. Similarly, after removing the communities, the two rules at router $B$ are merged into a single rule.

@@

Even when programming the network centrally, it is possible for operators to make mistakes and write incorrect policies.
\sysname includes many analyses to identify common mistakes at compile time. A subset includes: (i) a preference analysis to determine when backup paths/preferences will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining both the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find aggregates that do not summarize any specific prefix.

@@

We found that we could translate all network policies to \sysname. We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname. The datacenter operator said that he found the language intuitive. The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We further found that the datacenter policies were correctly translated. For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
%
For both the datacenter and backbone networks, the \sysname compiler was able to guarantee policy-compliance under all possible failure scenarios.

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for datacenter and backbone networks of different sizes. For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on predicates in parallel. A single predicate can describe many prefixes, for example by matching on a disjunction of prefixes. At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the datacenter network and 45 seconds for the backbone network.

@@

Total compilation for the largest datacenter is less than 9 minutes total. Unlike the datacenter policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network, takes less than 3 minutes total. The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn leads to PGIR construction and minimization taking proportionally more time.

@@

We comment briefly on how \sysname-generated configurations differ from configurations or templates written by operators.
%
In some ways, \sysname configurations are similar. For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.

>>>>

\author{%
Ryan Beckett\\
  \affaddr{Princeton}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{UCLA}
  %\affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and
Jitendra Padhye\\
  \affaddr{Microsoft}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton}
  %\\
  %\email{dpw@princeton.edu}
}

@@

The next step rewrites the high-level constraints such as $\Enter$ according to the equivalences in Figure~\ref{fig:rir-syntax}. Since preferences can only occur at the outermost level for an RIR expression, the final step is to ``lift" occurrences of the preference operator in each regular expression. For example, the regular expression $r \cdot (s \Prefer t) \cdot u$ is lifted to $(r \cdot s \cdot u) \Prefer (r \cdot t \cdot u)$ by distributing the preference over the sequence operator. In general, we employ the following distributivity equivalences:
%
\[
\begin{array}{c}
  r \odot (s_1 \Prefer \dots \Prefer s_n) = (r \odot s_1) \Prefer \dots \Prefer (r \odot s_n) \\
  (s_1 \Prefer \dots \Prefer s_n) \odot r = (s_1 \odot r) \Prefer \dots \Prefer (s_n \odot r)
\end{array}
\]
%
where $\odot$ stands for an arbitrary regular binary operator, and $r$ is a policy with a single preference.
%
In cases where $r$ does not contain a single preference, such as $(s ~\Prefer~ t) \cdot (u ~\Prefer~ v)$, it is not clear which of the paths $s \cdot v$ or $t \cdot u$ is preferred. \sysname rejects such ambiguous policies, requiring instead that operators explicitly specify which paths to prefer --- for example as $(s \cdot u) ~\Prefer~ (s \cdot v) ~\Prefer~ (t \cdot u) ~\Prefer~ (t \cdot v)$.
%
Policies that contain preferences nested under a unary operator (\IE, \textit{star} or \textit{negation}) are also rejected by \sysname as invalid.

@@

@@

As shown in \S\ref{sec:motivation}, aggregation can lead to subtle black-holing of traffic when failures occur. Determining when this can happen requires knowledge, not only of the topology, but also of the policy. For instance, a policy might require that all traffic for a particular prefix go over a single link before being aggregated. If that one link fails, a black hole might be introduced.
%
Because the PGIR encodes the complete user policy and topology, \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.

@@

For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the PGIR for \CD{PG1}. Since we know aggregation will occur at $X$, and that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first and woul then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is now disconnected from $X$, 2 is a lower bound on the number of failures required to introduce an aggregation black hole for prefix \CD{PG1}. This process is repeated for other aggregation locations (\EG, $Y$).

@@

@@

Finally, the external AS $W$ should prefer our internal router $A$ over $B$. In general, it is not possible to reliably control traffic entering the network beyond certain special cases. In this example, however, assuming our network and $W$ have an agreement to honor MEDs, the MED attribute can influence $W$ to prefer $A$ over $B$. Additionally, the compiler can use the BGP no-export community to ensure that no other AS beyond $W$ can send us traffic. The compiler performs a simple analysis to determine when it can utilize BGP special attributes to ensure traffic enters the network in a particular way by looking at links in the product graph that cross from the internal topology to the external topology.
%Aggregation is another tool commonly used to influence how traffic can enter the network, by relying on BGP's longest prefix matching default. Since aggregates are provided as additional user constraints, the compiler can also make use of this information to check that incoming preferences can be met given the aggregates specified (e.g., to ensure that all external ASes prefer to enter from one location over another).
Figure~\ref{fig:abgp-config} shows the full configuration from the compilation example.

After configuration generation, the compiler further processes the ABGP policy, removing community tags when possible, combining filters, removing dead filters, and so on. In the compilation example all community tags can be removed, since there is never any ambiguity based on the router importing the route and the neighbor the route is being imported from. After removing the communities, the two rules at router $B$ are merged into a single rule.

@@

Even when programming the network centrally, it is possible for operators to make mistakes.
\sysname includes many analyses to identify common mistakes at compile time. A subset includes: (i) a preference analysis to determine when backup paths will never be used, (ii) a reachability analysis to check if locations that should be reachable according to the policy are not reachable after combining the topology and policy, (iii) an anycast analysis to find instances where the operator might accidentally anycast a prefix (\IE, originates the prefix from multiple locations), (iv) an aggregate analysis to find unused aggregates that do not summarize any specific prefix.

@@

We found that we could translate all network policies to \sysname. We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname. The datacenter operator said that he found the language intuitive. The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} 
%We further found that the datacenter policies were correctly translated. 
For the backbone network, the operator mentioned an additional policy not present in the English document, which we added later.
%
For both the datacenter and backbone networks, \sysname was able to guarantee policy-compliance under all possible failure scenarios.

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for datacenter and backbone networks of different sizes. For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each predicate in parallel. A single predicate can describe many prefixes, for example by matching on a disjunction of prefixes. At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the datacenter network and 45 seconds for the backbone network.

@@

Compilation for the largest datacenter takes less than 9 minutes total. Unlike the datacenter policy, the number of predicates for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network takes less than 3 minutes total. The inclusion of both more preferences and more neighboring ASes in the backbone policy increases the size of the resulting PGIR, which in turn leads to PGIR construction and minimization taking proportionally more time.

@@

We comment briefly on how \sysname-generated configurations differ from configurations written by operators.
%
In some ways they are similar. For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.
